---
title: "Causal Verbs Analysis for Binary Rock Exp"
# output: html_document
output: rmarkdown::github_document
---
## Load libraries
```{r load libraries}
# install.packages("tidyverse")
# install.packages("Hmisc")
library(tidyverse)
library(here)
library(writexl)

theme_set(theme_bw())
```


## Load data
```{r}
# df_import = read_csv(here("data_analysis", "test_data.csv"))
df_import=read_csv("data1.csv", show_col_types = TRUE) %>%
  filter(submission_id>292) 
# glimpse(df_import)
# view(df_import)
```
```{r}
df_postQuest = df_import %>%
  select(submission_id,comments, education, gender, languages)
unique(df_postQuest$comments)
```
## Gentle preprocessing
More things to be written
```{r}
library(plyr)
df_main = df_import %>%
 
  dplyr::rename(anon_worker_id = submission_id,
          choice0 = `yesno-choice0`,
          choice1 = `yesno-choice1`,
          choice2 = `yesno-choice2`,
          choice3 = `yesno-choice3`,
          choice4 = `yesno-choice4`) %>%
  select(anon_worker_id, RT, startTime, endTime, picture, question0, question1, question2, question3, question4, 
          trial_number, choice0, choice1, choice2, choice3, choice4) %>%
  mutate_at(vars(picture), funs(str_replace_all(., "(images/|\\.gif)", ""))) %>%
  mutate(condition = case_when(
    picture == 'DOWNHazard100UPHazard0' ~ "Removes rock, prefers apple, reaches apple.",
    picture == 'DOWNHazard100DOWNHazard0' ~ "Removes rock, prefers banana, reaches banana.",
    picture == 'UPHazard0DOWNHazard100' ~ "Places rock, prefers apple, reaches banana.",
    picture == "DOWNHazard0DOWNHazard100" ~ "Places rock, prefers banana, reaches banana.",
    picture == 'DOWNHazard100DOWNHazard100' ~ "Doesn't remove rock, prefers ?, reaches banana.",
    picture == 'UPHazard0UPHazard0' ~ "Doesn't place rock, prefers apple, reaches apple.", 
    picture == "DOWNHazard0DOWNHazard0" ~ "Doesn't place rock, prefers banana, reaches banana."
  ))

glimpse(df_import) 
```
# Attention check function
Ignores the trials where participants did not pass the attention check
```{r}
movedpictures <- c('DOWNHazard100UPHazard0','DOWNHazard100DOWNHazard0','UPHazard0DOWNHazard100',"DOWNHazard0DOWNHazard100")
  nomovedpictures <- c('DOWNHazard100DOWNHazard100','UPHazard0UPHazard0', "DOWNHazard0DOWNHazard0")
  
  df_attention <- df_main %>%
    mutate(attention_answer = case_when(
      str_detect(question0, "<strong>moved</strong>") ~ choice0,
      str_detect(question1, "<strong>moved</strong>") ~ choice1,
      str_detect(question2, "<strong>moved</strong>") ~ choice2,    
      str_detect(question3, "<strong>moved</strong>") ~ choice3,
      str_detect(question4, "<strong>moved</strong>") ~ choice4,
      TRUE ~ "NA")) %>%
    mutate(attention_check = case_when(
      attention_answer == "yes" & picture %in% movedpictures ~ TRUE,
      attention_answer == "no" & picture %in% nomovedpictures ~ TRUE,
      TRUE ~ FALSE)) %>%
    group_by(anon_worker_id) %>%
    mutate(trialsPassed = sum(attention_check)) %>%
    ungroup() %>%
    filter(trialsPassed>6)
  
  table(df_attention$picture,df_attention$attention_check)
  
  # view(df_attention)
```
# Checking how many instances of each verb
```{r}
allowed_length=length(grep("<strong>allowed</strong>", df_attention$question0))+
  length(grep("<strong>allowed</strong>", df_attention$question1))+
  length(grep("<strong>allowed</strong>", df_attention$question2))+
  length(grep("<strong>allowed</strong>", df_attention$question3))+
  length(grep("<strong>allowed</strong>", df_attention$question4))
print(paste("Allowed = ", toString(allowed_length)))

let_length=length(grep("<strong>let</strong>", df_attention$question0))+
  length(grep("<strong>let</strong>", df_attention$question1))+
  length(grep("<strong>let</strong>", df_attention$question2))+
  length(grep("<strong>let</strong>", df_attention$question3))+
  length(grep("<strong>let</strong>", df_attention$question4))
print(paste("Let = ", toString(let_length)))

enabled_length=length(grep("<strong>enabled</strong>", df_attention$question0))+
  length(grep("<strong>enabled</strong>", df_attention$question1))+
  length(grep("<strong>enabled</strong>", df_attention$question2))+
  length(grep("<strong>enabled</strong>", df_attention$question3))+
  length(grep("<strong>enabled</strong>", df_attention$question4))
print(paste("Enabled = ", toString(enabled_length)))

caused_length=length(grep("<strong>caused</strong>", df_attention$question0))+
  length(grep("<strong>caused</strong>", df_attention$question1))+
  length(grep("<strong>caused</strong>", df_attention$question2))+
  length(grep("<strong>caused</strong>", df_attention$question3))+
  length(grep("<strong>caused</strong>", df_attention$question4))
print(paste("Caused = ", toString(caused_length)))

made_length=length(grep("<strong>made</strong>", df_attention$question0))+
  length(grep("<strong>made</strong>", df_attention$question1))+
  length(grep("<strong>made</strong>", df_attention$question2))+
  length(grep("<strong>made</strong>", df_attention$question3))+
  length(grep("<strong>made</strong>", df_attention$question4))
print(paste("Made = ", toString(made_length)))

got_length=length(grep("<strong>got</strong>", df_attention$question0))+
  length(grep("<strong>got</strong>", df_attention$question1))+
  length(grep("<strong>got</strong>", df_attention$question2))+
  length(grep("<strong>got</strong>", df_attention$question3))+
  length(grep("<strong>got</strong>", df_attention$question4))
print(paste("Got = ", toString(got_length)))

prevented_length=length(grep("<strong>prevented</strong>", df_attention$question0))+
  length(grep("<strong>prevented</strong>", df_attention$question1))+
  length(grep("<strong>prevented</strong>", df_attention$question2))+
  length(grep("<strong>prevented</strong>", df_attention$question3))+
  length(grep("<strong>prevented</strong>", df_attention$question4))
print(paste("Prevented = ", toString(prevented_length)))

stopped_length=length(grep("<strong>stopped</strong>", df_attention$question0))+
  length(grep("<strong>stopped</strong>", df_attention$question1))+
  length(grep("<strong>stopped</strong>", df_attention$question2))+
  length(grep("<strong>stopped</strong>", df_attention$question3))+
  length(grep("<strong>stopped</strong>", df_attention$question4))
print(paste("Stopped = ", toString(stopped_length)))

blocked_length=length(grep("<strong>blocked</strong>", df_attention$question0))+
  length(grep("<strong>blocked</strong>", df_attention$question1))+
  length(grep("<strong>blocked</strong>", df_attention$question2))+
  length(grep("<strong>blocked</strong>", df_attention$question3))+
  length(grep("<strong>blocked</strong>", df_attention$question4))
print(paste("Blocked = ", toString(blocked_length)))

#Allowed: 259
#Let: 225
#Enabled: 189
#Caused: 182
#Made: 196
#Got: 280
#Prevented: 273
#Stopped: 196
#Blocked: 203
```

# Plotting RT against trial number
Does the trial number that the participant is completing affect how long it takes them to complete the trial?
```{r}
df_main %>%
  select(trial_number, RT) %>%
  ggplot(., aes(x=trial_number, y=RT)) +
    geom_point(size=3, alpha=0.5) +
    stat_summary(fun.data = "mean_cl_boot",
                 geom = "errorbar",
                 width = 0.2,
                 color = "grey") +
    stat_summary(fun = "mean", 
                 geom = "point",
                 color = "red",
                 size = 5) +
    xlab("Trial Number") +
    ylab("Reaction Time\n(in milliseconds)") +
    theme(axis.text = element_text(size=12),
          axis.title = element_text(size=15))
```

```{r}
# glimpse(df_main)

df_clean = df_main %>%
  select(anon_worker_id, question0, question1, question2, question3, question4, 
        choice0, choice1, choice2, choice3, choice4, picture, condition) %>%
  mutate(got = case_when(
    str_detect(question0, "<strong>got</strong>") ~ choice0,
    str_detect(question1, "<strong>got</strong>") ~ choice1,
    str_detect(question2, "<strong>got</strong>") ~ choice2,
    str_detect(question3, "<strong>got</strong>") ~ choice3,
    str_detect(question4, "<strong>got</strong>") ~ choice4,
    TRUE ~ "NA"
  )) %>%
  mutate(allowed = case_when(
    str_detect(question0, "<strong>allowed</strong>") ~ choice0,
    str_detect(question1, "<strong>allowed</strong>") ~ choice1,
    str_detect(question2, "<strong>allowed</strong>") ~ choice2,
    str_detect(question3, "<strong>allowed</strong>") ~ choice3,
    str_detect(question4, "<strong>allowed</strong>") ~ choice4,
    TRUE ~ "NA"
  )) %>%
  # TODO: to the other verbs
  mutate(made = case_when(
    str_detect(question0, "<strong>made</strong>") ~ choice0,
    str_detect(question1, "<strong>made</strong>") ~ choice1,
    str_detect(question2, "<strong>made</strong>") ~ choice2,
    str_detect(question3, "<strong>made</strong>") ~ choice3,
    str_detect(question4, "<strong>made</strong>") ~ choice4,
    TRUE ~ "NA"
  )) %>%
  mutate(caused = case_when(
    str_detect(question0, "<strong>caused</strong>") ~ choice0,
    str_detect(question1, "<strong>caused</strong>") ~ choice1,
    str_detect(question2, "<strong>caused</strong>") ~ choice2,
    str_detect(question3, "<strong>caused</strong>") ~ choice3,
    str_detect(question4, "<strong>caused</strong>") ~ choice4,
    TRUE ~ "NA"
  )) %>%
  mutate(enabled = case_when(
    str_detect(question0, "<strong>enabled</strong>") ~ choice0,
    str_detect(question1, "<strong>enabled</strong>") ~ choice1,
    str_detect(question2, "<strong>enabled</strong>") ~ choice2,
    str_detect(question3, "<strong>enabled</strong>") ~ choice3,
    str_detect(question4, "<strong>enabled</strong>") ~ choice4,
    TRUE ~ "NA"
  )) %>%
  mutate(let = case_when(
    str_detect(question0, "<strong>let</strong>") ~ choice0,
    str_detect(question1, "<strong>let</strong>") ~ choice1,
    str_detect(question2, "<strong>let</strong>") ~ choice2,
    str_detect(question3, "<strong>let</strong>") ~ choice3,
    str_detect(question4, "<strong>let</strong>") ~ choice4,
    TRUE ~ "NA"
  )) %>%
  mutate(prevented = case_when(
    str_detect(question0, "<strong>prevented</strong>") ~ choice0,
    str_detect(question1, "<strong>prevented</strong>") ~ choice1,
    str_detect(question2, "<strong>prevented</strong>") ~ choice2,
    str_detect(question3, "<strong>prevented</strong>") ~ choice3,
    str_detect(question4, "<strong>prevented</strong>") ~ choice4,
    TRUE ~ "NA"
  )) %>%
  mutate(stopped = case_when(
    str_detect(question0, "<strong>stopped</strong>") ~ choice0,
    str_detect(question1, "<strong>stopped</strong>") ~ choice1,
    str_detect(question2, "<strong>stopped</strong>") ~ choice2,
    str_detect(question3, "<strong>stopped</strong>") ~ choice3,
    str_detect(question4, "<strong>stopped</strong>") ~ choice4,
    TRUE ~ "NA"
  )) %>%
  mutate(blocked = case_when(
    str_detect(question0, "<strong>blocked</strong>") ~ choice0,
    str_detect(question1, "<strong>blocked</strong>") ~ choice1,
    str_detect(question2, "<strong>blocked</strong>") ~ choice2,
    str_detect(question3, "<strong>blocked</strong>") ~ choice3,
    str_detect(question4, "<strong>blocked</strong>") ~ choice4,
    TRUE ~ "NA"
  )) %>%
  select(anon_worker_id, got, allowed, made, caused, enabled, let, prevented, stopped, blocked, picture, condition)

  glimpse(df_clean)
  
  write.csv(df_clean,"english_cleaned.csv", row.names = FALSE)


```

```{r}
fun_mean <- function(x){return(round(data.frame(y=mean(x),label=mean(x,na.rm=T)),digit=2))}

df_tidy = df_clean %>%
  gather(verbs, rating, -anon_worker_id, -picture, -condition) %>%
  filter(rating != "NA") %>%
  mutate_at(vars(rating), funs(case_when(
    rating == "no" ~ 0,
    rating == "yes" ~ 1,
    TRUE ~ 404
  ))) 
df_tidy %>%
  mutate_at(vars(verbs), funs(fct_relevel(.,c("caused", "got", "made", "enabled", "let", "allowed", "prevented", "stopped", "blocked")))) %>%
  mutate_at(vars(condition), funs(fct_relevel(.,c("Places rock, prefers apple, reaches banana.", 
                                                  "Places rock, prefers banana, reaches banana.",
                                                  "Removes rock, prefers apple, reaches apple.",
                                                  "Removes rock, prefers banana, reaches banana.",
                                                  "Doesn't place rock, prefers apple, reaches apple.",
                                                  "Doesn't place rock, prefers banana, reaches banana.")))) %>%
  ggplot(., aes(x=verbs, y=rating)) +
    facet_wrap(vars(condition), nrow=4) +
    stat_summary(fun = "mean", 
                 geom = "bar",
                 color = "black",
                 fill = "lightblue",
                 width = .5) +
    # stat_summary(fun.data = fun_mean, geom="text", vjust=-0.7, size=1) +
    stat_summary(fun.data = "mean_cl_boot",
                   geom = "errorbar",
                   width = 0.2,
                   color = "grey")


```
# Long Form
Gets long form of data by combining verb columns
```{r}
df_clean %>%
  gather(verbs, rating, -anon_worker_id, -picture) %>%
  filter(rating != "NA") %>%
  ggplot(., aes(x=verbs, fill=rating)) +
    facet_wrap(vars(picture), nrow=4) +
    geom_bar(stat="count", position=position_dodge())
```
```{r}
averages <- tapply(df_tidy$rating, list(df_tidy$verbs, df_tidy$condition), mean)

std <- tapply(df_tidy$rating, list(df_tidy$verbs, df_tidy$condition), sd)

se <- std/sqrt(72)

alpha <- 0.05
degrees.freedom = 72 - 1
t.score = qt(p=alpha/2, df=degrees.freedom,lower.tail=F)

margin_error <- t.score * se

df_prevent_ex <- filter(df_tidy, verbs == "prevented" & condition=="Places rock, prefers banana, reaches banana.")
  
df_stopped_ex <- filter(df_tidy, verbs == "stopped" & condition=="Places rock, prefers banana, reaches banana.")

```


```{r}
unique(df_tidy$condition)
unique(df_tidy$verbs)
glimpse(df_tidy)
```

```{r}
# average_e_cause <- tapply(df_tidy$rating, list(df_tidy$verbs=="caused" or "made" or "got", df_tidy$condition=="Doesn't place rock, prefers apple, reaches apple."), mean)
average_e_cause <- tapply(df_tidy$rating==TRUE, list(df_tidy$verbs %in% c("caused", "made", "got"), df_tidy$condition=="Doesn't place rock, prefers apple, reaches apple."), mean)
average_e_cause

average_e_enable <- tapply(df_tidy$rating==TRUE, list(df_tidy$verbs %in% c("enabled", "allowed", "let"), df_tidy$condition=="Doesn't place rock, prefers apple, reaches apple."), mean)
average_e_enable

average_f_enable <- tapply(df_tidy$rating==TRUE, list(df_tidy$verbs %in% c("enabled", "allowed", "let"), df_tidy$condition=="Doesn't place rock, prefers banana, reaches banana."), mean)
average_f_enable

average_g_prevent <- tapply(df_tidy$rating==TRUE, list(df_tidy$verbs %in% c("stopped", "prevented", "blocked"), df_tidy$condition=="Doesn't remove rock, prefers ?, reaches banana."), mean)
average_g_prevent
```
## Hypothesis 1

```{r}
#figure e
result1 = df_tidy %>% 
  filter(condition=="Doesn't place rock, prefers apple, reaches apple.") %>% 
  filter(verbs %in% c("caused", "made", "got")) 

result1 = result1 %>%
  aggregate(rating ~ anon_worker_id, FUN = mean)

result1$condition <- "Doesn't place rock, prefers apple, reaches apple."
result1$verbs <- "causing"

#figure e
result2 = df_tidy %>%
  filter(condition=="Doesn't place rock, prefers apple, reaches apple.") %>%
  filter(verbs %in% c("enabled", "allowed", "let"))

result2 = result2 %>%
  aggregate(rating ~ anon_worker_id, FUN = mean)

result2$condition <- "Doesn't place rock, prefers apple, reaches apple."
result2$verbs = "enabling"

#figure f
result3 = df_tidy %>%
  filter(condition=="Doesn't place rock, prefers banana, reaches banana.") %>%
  filter(verbs %in% c("enabled", "allowed", "let"))

result3 = result3 %>%
  aggregate(rating ~ anon_worker_id, FUN = mean)

result3$condition <- "Doesn't place rock, prefers banana, reaches banana."
result3$verbs = "enabling"

#figure g
result4 = df_tidy %>%
  filter(condition=="Doesn't remove rock, prefers ?, reaches banana.") %>%
  filter(verbs %in% c("prevented", "stopped", "blocked"))

result4 = result4 %>%
  aggregate(rating ~ anon_worker_id, FUN = mean)

result4$condition <- "Doesn't remove rock, prefers ?, reaches banana."
result4$condition <- "preventing"
```

```{r}
prop_test_e_cause <- t.test(result1$rating, alternative = "greater", mu=0)
# Calculate degrees of freedom
length(result1$rating) - 1
prop_test_e_cause$p.value
prop_test_e_cause$statistic

prop_test_e_enable <- t.test(result2$rating, alternative = "greater", mu=0)
# Calculate degrees of freedom
length(result2$rating) - 1
prop_test_e_enable$p.value
prop_test_e_enable$statistic

# also relevant to hypothesis 2
prop_test_f_enable <- t.test(result3$rating, alternative = "greater", mu=0)
length(result3$rating) - 1
prop_test_f_enable$p.value
prop_test_f_enable$statistic

#also relevant to hypothesis 3
prop_test_g_prevent <- t.test(result4$rating, alternative = "greater", mu=0)
length(result4$rating) - 1
prop_test_g_prevent$p.value
prop_test_g_prevent$statistic
```

## Hypothesis 2
```{r}
#figure d
result5 = df_tidy %>% 
  filter(condition=="Removes rock, prefers banana, reaches banana.") %>% 
  filter(verbs %in% c("enabled", "allowed", "let"))

result5 = result5 %>%
  aggregate(rating ~ anon_worker_id, FUN = mean)

result5$condition <- "Removes rock, prefers banana, reaches banana."
result5$verbs <- "enabling"

prop_test_d_enable <- t.test(result5$rating, alternative = "greater", mu=0)
length(result5$rating) - 1
prop_test_d_enable$p.value
prop_test_d_enable$statistic

```
## Hypothesis 3
```{r}
#figure b
result6 = df_tidy %>%
  filter(condition=="Places rock, prefers banana, reaches banana.") %>%
  filter(verbs %in% c("prevented", "stopped", "blocked")) 

result6 = result6 %>%
  aggregate(rating ~ anon_worker_id, FUN = mean)

result6$condition <- "Places rock, prefers banana, reaches banana."
result6$verbs <- "preventing"

prop_test_b_prevent <- t.test(result6$rating, alternative = "greater", mu=0)
length(result6$rating) - 1
prop_test_b_prevent$p.value
prop_test_b_prevent$statistic
```
